Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 intro.tex
small tweak in Introduction

Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower \NOTE{the extension cost?} of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building supercomputers with millions of cores.
Even with such powerful networks, 
intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
%An ideal job placement policy should not only load balance the network 
%but also guarantee the performance of every single application by minimizing the inevitable interference on the dragonfly network.

>>>>

Low-latency and high-bandwidth interconnect networks play a critical role in ensuring HPC system performance. 
The high-radix, low-diameter dragonfly topology can lower the overall cost of the interconnect, improve network bandwidth and reduce packet latency \cite{dally-dragonfly}, 
making it a very promising choice for building supercomputers with millions of cores.
Even with such powerful networks, 
intelligent job placement is of paramount importance to the efficient use of dragonfly connected systems~\cite{bhatele2015, jain-sc14}. 
%An ideal job placement policy should not only load balance the network 
%but also guarantee the performance of every single application by minimizing the inevitable interference on the dragonfly network.
